MIGRACE DAT - DEMUS / MUSEION

### 2023-02-15 NM_MDH_migrace.Rmd
NM-HM, quotes corrected, misto vzniku WIP

# install.packages("tidyverse", dependencies = T)
# install.packages("readxl")
# install.packages("stringr") # ::str_split_fixed
# install.packages("lubridate")
require(tidyverse)
require(readxl)
require(stringr) # ::str_pad
require(lubridate)

@@

project <- "MDH"

@@

path_data <- paste0(path, "data/")
path_csv <- paste0(path, "mus_csv/", project, "/")

@@

sbirky <- read_excel(paste0(path_data, "Sbirky.xlsx"))

@@

## Užitečné příkazy

```{r REMOVE ALL WORKING LAYERS, warning=F}

rm(demus_tab)
rm(modify_tab)
rm(mus_tab)
```

```{r SPLIT STRING, warning=F}

# # Split name column into firstname and last name
# df[c('First Name', 'Last Name')] <- str_split_fixed(df$Name, ' ', 2)
#  
# # Rearrange columns and remove original name column
# df <- df[c('First Name', 'Last Name', 'State')]

@@

**DEMUS**: Fondy  
**MUSEION**: csv_fond.csv

@@

write.table(mus_tab, paste0(path_csv, project, "_csv_fond.csv"), 
            sep = ";", quote = F, row.names = F, 
            na = "", fileEncoding="cp1250")

@@

@@

**DEMUS**: Skupiny  
**MUSEION**: csv_skupiny.csv

@@

write.table(mus_tab, paste0(path_csv, project, "_csv_skupiny.csv"), 
            sep = ";", quote = F, row.names = F, 
            na = "", fileEncoding="cp1250")

@@

@@

**DEMUS**: Adresar  
**MUSEION**: csv_adresar.csv

@@

demus_tab <- read_excel(paste0(path_data, "Adresar.xlsx"))
demus_tab[is.na(demus_tab)] <- ""

@@

modify_tab <- demus_tab %>% 
  mutate(MEMPTY = "") %>% 
  mutate('1typSubjektuKod' = "OO") %>% 
  mutate('2subjektKod' = paste(Prijmeni_A, Jmeno_A)) %>% 
  mutate('10osobaPohlavi' = "neznámé") %>%  # povinne: "muž", "žena", "neznámé"
  mutate('18subjektStatKod' = "CZ")

@@

write.table(mus_tab, paste0(path_csv, project, "_csv_adresar.csv"), 
            sep = ";", quote = F, row.names = F, 
            na = "", fileEncoding="cp1250")

@@

@@

demus_tab <- read_excel(paste0(path_data, "Osobnosti.xlsx"))
demus_tab[is.na(demus_tab)] <- ""

@@

**DEMUS**: Osobnosti  
**MUSEION**: csv_oo.csv

@@

modify_tab <- demus_tab %>% 
  filter(MTYPOSOSBY == "OO") %>% 
  mutate(MKODOS = paste(MPRIJM, MJMENO)) %>% 
  mutate(MEMPTY = "") %>% 
  mutate('10osobaPohlavi' = "neznámé") %>% 
   # mutate('18subjektStatKod' = "CZ") %>% 
  mutate('42subjektSbirka' = sbirka) %>% 
  mutate('43subjektPodsbirka' = podsbirka)

@@

mus_tab <- modify_tab %>% 
  select('1typSubjektuKod' = MTYPOSOSBY,        # !! povinne !!
         '2subjektKod' = MKODOS,                # !! povinne !!
         '3subjektAlterKod' = MEMPTY, '4osobaJmenoPrvni'= MJMENO, 
         '5osobaJmenoDruhe' = MDRJMENO, 
         '6osobaPrijmeni' = MPRIJM,             # !! povinne !!
         '7osobaTitulPredJmenem' = MTITULPRED, '8osobaTitulZaJmenem' = MEMPTY, 
         '9osobaRodnePrijmeni' = MEMPTY, 
         '10osobaPohlavi' = '10osobaPohlavi',   # !! povinne !! "muž", "žena", "neznámé"
         '11osobaDatumNarozeni' = DatNar_OS, '12osobaMistoNarozeni' = MistoNar_OS,
         '13okresNarozeniNazev' = MEMPTY, '14obecNarozeniNazev' = MEMPTY,
         '15statNarozeniKod' = MEMPTY, '16osobaDatumUmrti' = DatUmr_OS,
         '17osobaMistoUmrti' = MistoUmr_OS, '18subjektStatKod' = MEMPTY,
         '19kontaktEmail' = MEMPTY, '20kontaktMobil' = MEMPTY,
         '21kontaktMobil2' = MEMPTY, '22kontaktTelefon' = MEMPTY,
         '23kontaktInternet' = MEMPTY, '24kontaktInternetoveVolani' = MEMPTY,
         '25adresaText' = MEMPTY, '26kontaktniAdresaText' = MEMPTY,
         '27fyzickaOsobaRodneCislo' = MEMPTY, '28subjektPoznamka' = MEMPTY,
         '29AdresaTextoveOkres' = MEMPTY, '30AdresaTextoveObec' = MEMPTY,
         '31AdresaTextoveCastObce' = MEMPTY, '32AdresaTextoveMestskaCast' = MEMPTY,
         '33AdresaTextoveUlice' = MEMPTY, '34AdresaTextoveCisloOrientacni' = MEMPTY,
         '35AdresaTextoveCislo' = MEMPTY, '36AdresaTextovePSC' = MEMPTY,
         '37zamestnanecCislo' = MEMPTY, '38oddeleniKod' = MEMPTY,
         '39osobnostMedailon' = Medailon_OS, '40osobnostPseudonym' = MEMPTY,
         '41okruhSubjektuNazev' = MEMPTY,

@@

         '44osobaStudia' = MEMPTY,
         '45osobaSpolky' = MEMPTY, '46osobaOsobnost' = MEMPTY,
         '47subjektDatumOd' = MEMPTY, '48subjektDatumDo' = MEMPTY,
         '49kontaktEmail2' = MEMPTY, 
         '50text1' = MEMPTY, '51text2' = MEMPTY, '52text3' = MEMPTY, 
         '53role1' = MEMPTY, '54role2' = MEMPTY, 
         '55role3' = MEMPTY, '56role4' = MEMPTY, '57$role5' = MEMPTY) %>% 
  mutate_all( ~ str_replace_all(., pattern = ";", replacement = " ")) %>% # removes semicolons
  mutate_all( ~ str_replace_all(., pattern = "[\r\n]", replacement = " ")) #removes paragraphs

write.table(mus_tab, paste0(path_csv, project, "_csv_oo.csv"), 
            sep = ";", quote = F, row.names = F, 
            na = "", fileEncoding="cp1250")

oper_oo <- mus_tab

@@

**DEMUS**: Osobnosti  
**MUSEION**: csv_po.csv

@@

mus_tab <- modify_tab %>% 
  select(
    '1subjektKod' = '1subjektKod',          # !! povinne !!
    '2subjektAlterKod'= MEMPTY,
    '3pravnickaOsobaNazev' = Jmeno_OS,      # !! povinne !!
    '4pravnickaOsobaIC'= MEMPTY,
    '5pravnickaOsobaDIC' = MEMPTY, '6pravnickaOsobaZapsan'= MEMPTY,
    '7pravnickaOsobaFOP' = MEMPTY, '8subjektStatKod'= MEMPTY,
    '9kontaktEmail' = MEMPTY, '10kontaktMobil'= MEMPTY,
    '11kontaktMobil2' = MEMPTY, '12kontaktTelefon'= MEMPTY,
    '13kontaktInternet' = MEMPTY, '14kontaktInternetoveVolani'= MEMPTY,
    '15adresaText' = MEMPTY, '16kontaktniAdresaText'= MEMPTY,
    '17subjektPoznamka' = MEMPTY, '18AdresaTextoveOkres'= MEMPTY,
    '19AdresaTextoveObec' = MEMPTY, '20AdresaTextoveCastObce'= MEMPTY,
    '21AdresaTextoveMestskaCast' = MEMPTY, '22AdresaTextoveUlice'= MEMPTY,
    '23AdresaTextoveCisloOrientacni' = MEMPTY, '24AdresaTextoveCislo'= MEMPTY,
    '25AdresaTextovePSC' = MEMPTY,  '26subjektSbirka'= '26subjektSbirka',           
    '27subjektPodsbirka' = '27subjektPodsbirka', '28subjektDatumOd'= MEMPTY,
    '29subjektDatumDo' = MEMPTY, '30subjektMedailon'= Medailon_OS,
    '31okruhSubjektuNazev' = MEMPTY, '32kontaktEmail2'= MEMPTY,
    '33text1' = MEMPTY, '34text2'= MEMPTY,'35text3' = MEMPTY, 
    '36role1'= MEMPTY, '37role2' = MEMPTY, '38role3'= MEMPTY,
    '39role4' = MEMPTY, '40role5'= MEMPTY)

write.table(mus_tab, paste0(path_csv, project, "_csv_po.csv"), 
            sep = ";", quote = F, row.names = F, 
            na = "", fileEncoding="cp1250")

oper_po <- mus_tab

@@

**DEMUS**: Lokality  
**MUSEION**: csv_lokalita.csv

@@

# write.table(mus_tab, paste0(path_csv, project, "_csv_lokalita.csv"), 
#             sep = ";", quote = F, row.names = F, 
#             na = "", fileEncoding="cp1250")

@@

@@

**DEMUS**: Materialy  
**MUSEION**: csv_material.csv

@@

write.table(mus_tab, paste0(path_csv, project, "_csv_material.csv"), 
            sep = ";", quote = F, row.names = F, 
            na = "", fileEncoding="cp1250")

@@

@@

**DEMUS**: Techniky  
**MUSEION**: csv_technika.csv

@@

write.table(mus_tab, paste0(path_csv, project, "_csv_technika.csv"), 
            sep = ";", quote = F, row.names = F, 
            na = "", fileEncoding="cp1250")

@@

@@

**DEMUS**: Nazvy 
**MUSEION**: csv_oznaceni.csv

@@

write.table(mus_tab, paste0(path_csv, project, "_csv_oznaceni.csv"), 
            sep = ";", quote = F, row.names = F, 
            na = "", fileEncoding="cp1250")

@@

@@

## Datace

**DEMUS**: Sbirky 
**MUSEION**: csv_dataceNazvem.csv

**IMPORTNÍ ROZHRANNÍ**: CSV Datace názvem

```{r EXTRACT DATATION FROM TABLE SBIRKY, warning = F}

modify_tab <- sbirky

```{r CREATE CSV DATACE NAZVEM}

# mus_tab <- modify_tab %>% 
#   select(
#     '1sbirkaCisloEvidInt' = '1sbirkaCisloEvidInt', # !! povinne !!
#     '2podsbirkaCislo'= '2podsbirkaCislo',          # !! povinne !!
#     '3materialovaSkupinaKod' = MEMPTY, 
#     '4oznaceniNazev'= Nazev_NZ,                   # !! povinne !!
#     '5oznaceniPoznamka' = Pozn_NZ)
# 
# write.table(mus_tab, paste0(path_csv, project, "_csv_dataceNazvem.csv"), 
#             sep = ";", quote = F, row.names = F, 
#             na = "", fileEncoding="cp1250")
# 
# oper_datace <- mus_tab

SELECT "" As 1sbirkaCisloEvidInt, "" As 2podsbirkaCislo, "" As 3dataceNazvemNazev, "" As 4dataceHodnota, "" As 5dataceSnad, "" As 6kvalifikatorDataceNazev, "" As 7dataceSnad2, "" As 8kvalifikatorDatace2Nazev, "" As 9dataceNazvemPoznamka, "" As 10dataceNazvemPublicNadNazev, "" As 11dataceNazvemPublicNaz FROM TABULKA;

@@

**DEMUS**: Sbirky  
**MUSEION**: csv_matpred.csv

@@

write.table(mus_tab, paste0(path_csv, project, "_csv_matpred.csv"), 
            sep = ";", quote = F, row.names = F, 
            na = "", fileEncoding="cp1250")

@@

@@

**DEMUS**: Sbirky 
**MUSEION**: csv_techpred.csv

@@

write.table(mus_tab, paste0(path_csv, project, "_csv_techpred.csv"), 
            sep = ";", quote = F, row.names = F, 
            na = "", fileEncoding="cp1250")

@@

@@

tabulka s trojici ke konkretnimu predmetu
invc1 - 1. autor
invc1 - 1. datace
invc1 - 1. misto vzniku
invc1 - 2. autor 2
invc2 - 2. datace 2, atd

### role

@@

```{r CHECK ROLES AND LOCS DICTIONARIES}

@@

```{r CHECK ROLES AND LOCS DICTIONARIES}
# roles
unique(sbirky$Role_S)

# locations
unique(oper_lokalita$'1lokalitaNazev')
unique(sbirky$MistoVz_S)

write.table(mvzn_tab, paste0(path_csv, project, "_csv_lokalita_MVZN.csv"),
            sep = ";", quote = F, row.names = F,
            na = "", fileEncoding="cp1250")

@@

**DEMUS**: Sbirky 
**MUSEION**: csv_vznikPtu.csv

@@

```{r DERIVE VZNIKPTU FROM SBIRKY, warning = F}

dopr_tab <- sbirky %>% 
  select(MINVC, Autor_S, Role_S, Datace_S, MistoVz_S) %>% 
  mutate(MEMPTY = "") %>% 
  mutate(MDATACE = Datace_S) %>% 
  mutate(MDAT_Y = ifelse(str_detect(MDATACE, "_00_00"), MDATACE, "")) %>% 
  mutate(MDAT_Y = str_replace_all(MDAT_Y, "_00|-00", ""))

ym <- dopr_tab %>% 
  # mutate(MDAT_YM = ifelse(str_detect(MDATACE, "/^[^_]*_[^_]*_*00$/"), MDATACE, "")) 
  # mutate(MDAT_YM = ifelse(str_detect(MDATACE, "\\w*_*[^0]*[^0]*_*\\w"), MDATACE, "")) 
  mutate(MDAT_YM = ifelse(str_detect(MDATACE, "\\.(00_00)$"), "", MDATACE))

  mutate(MDATACE = str_replace_all(dopr_tab$MDATACE, "-00", "")) %>% 
  mutate(MDAT_LATER = ifelse(str_detect(dopr_tab$MDATACE, "XX"), dopr_tab$MDATACE, "")) %>% 
  mutate('2poradi' = "") %>% 
  mutate('15dataceSnad' = ifelse(str_detect(dopr_tab$MDATACE, "\\?"), 1, 0))

@@

```{r CREATE CSV VZNIKPTU}

@@

write.table(mus_tab, paste0(path_csv, project, "_csv_vznikPtu.csv"), 
            sep = ";", quote = F, row.names = F, 
            na = "", fileEncoding="cp1250")

@@

@@

**DEMUS**: Sbirky 
**MUSEION**: csv_obp.csv

@@

    '115rokPrirust' = MEMPTY,'116mnozstviSlovy' = MEMPTY,
    '117pocetCasti' = MEMPTY,'118popisCasti' = MEMPTY) %>% 
  mutate_all( ~ str_replace_all(., pattern = ";", replacement = " ")) %>%  # removes semicolons
  mutate_all( ~ str_replace_all(., pattern = "[\r\n]", replacement = " ")) # removes paragraphs

# write table

write.table(mus_tab, paste0(path_csv, project, "_csv_obp.csv"), 
            sep = ";", quote = F, row.names = F, 
            na = "", fileEncoding="cp1250")

@@

@@

write.table(mus_tab_cvic, paste0(path_csv, project, "_csv_obp_cv.csv"),
            sep = ";", quote = F, row.names = F,
            na = "", fileEncoding="cp1250")
```

@@

**DEMUS**: Sbirky 
**MUSEION**: csv_par.csv

@@

write.table(mus_tab, paste0(path_csv, project, "_csv_par.csv"), 
            sep = ";", quote = F, row.names = F, 
            na = "", fileEncoding="cp1250")
```

@@

**DEMUS**: Sbirky 
**MUSEION**: csv_vum.csv

@@

write.table(mus_tab, paste0(path_csv, project, "_csv_vum.csv"), 
            sep = ";", quote = F, row.names = F, 
            na = "", fileEncoding="cp1250")

@@

**DEMUS**: Sbirky 
**MUSEION**: csv_fot.csv

@@

write.table(mus_tab, paste0(path_csv, project, "_csv_fot.csv"), 
            sep = ";", quote = F, row.names = F, 
            na = "", fileEncoding="cp1250")

@@

**DEMUS**: Sbirky 
**MUSEION**: csv_bio.csv

@@

write.table(mus_tab, paste0(path_csv, project, "_csv_bio.csv"), 
            sep = ";", quote = F, row.names = F, 
            na = "", fileEncoding="cp1250")

@@

**DEMUS**: Sbirky 
**MUSEION**: csv_br.csv

@@

    '39nominaceRok' = MEMPTY, '40nominaceKategorie' = MEMPTY,
    '41oceneniRok' = MEMPTY, '42oceneniKategorie' = MEMPTY,
    '43oceneniMisto' = MEMPTY, '44oceneniTyp' = MEMPTY,
    '45variantaCCLicenceOznaceni' = MEMPTY, '46seznamKontextovychDokumen' = MEMPTY) %>% 
  mutate_all( ~ str_replace_all(., pattern = ";", replacement = " ")) %>%  # removes semicolons
  mutate_all( ~ str_replace_all(., pattern = "[\r\n]", replacement = " ")) #removes paragraphs

@@

write.table(mus_tab, paste0(path_csv, project, "_csv_br.csv"), 
            sep = ";", quote = F, row.names = F, 
            na = "", fileEncoding="cp1250")
```

@@

>>>>

# install.packages("tidyverse", dependencies = T)
# install.packages("readxl")
# install.packages("stringr") # ::str_split_fixed
# install.packages("lubridate")
# install.packages("anytime")
require(tidyverse)
require(readxl)
require(stringr) # ::str_pad
require(lubridate) 
require(anytime) # ::anydate

@@

spravce <- "NM-HM"
project <- "MDH"

@@

path_data <- paste0(path, "data/", project, "/")
path_csv <- paste0(path, "mus_csv/", spravce, "/", project, "/")

@@

sbirky <- read_excel(paste0(path_data, "/Sbirky.xlsx"))

@@

@@

**DEMUS**: Fondy  
**MUSEION**: import_fond.csv

@@

@@

# SAVE IMPORT FILE

save <- paste0(path_csv, spravce, "_import_fond.csv")

if(file.exists(save)){
  print("You've been here before!")
} else {
  write.table(mus_tab, file = save, 
            sep = ";", quote = T, row.names = F, 
            na = "", fileEncoding="cp1250")
  print("Written, baby!")
  }

@@

**DEMUS**: Skupiny  
**MUSEION**: import_skupiny.csv

@@

@@

# SAVE IMPORT FILE

save <- paste0(path_csv, spravce, "_import_skupiny.csv")

if(file.exists(save)){
  print("You've been here before!")
} else {
  write.table(mus_tab, file = save, 
            sep = ";", quote = T, row.names = F, 
            na = "", fileEncoding="cp1250")
  print("Written, baby!")
  }

@@

**DEMUS**: Adresar  
**MUSEION**: import_adresar.csv

@@

demus_tab <- read_excel(paste0(path_data, "/Adresar.xlsx"))
demus_tab[is.na(demus_tab)] <- ""

@@

modify_tab <- demus_tab %>% 
  mutate(MEMPTY = "") %>% 
  mutate('1typSubjektuKod' = "OO") %>% 
  mutate('2subjektKod' = str_trim(paste0(Prijmeni_A, " ", Jmeno_A))) %>% 
  mutate('10osobaPohlavi' = "neznámé") %>%  # povinne: "muž", "žena", "neznámé"
  mutate('18subjektStatKod' = "CZ")

@@

@@

# SAVE IMPORT FILE

save <- paste0(path_csv, spravce, "_import_adresar.csv")

if(file.exists(save)){
  print("You've been here before!")
} else {
  write.table(mus_tab, file = save, 
            sep = ";", quote = T, row.names = F, 
            na = "", fileEncoding="cp1250")
  print("Written, baby!")
  }

@@

demus_tab <- read_excel(paste0(path_data, "/Osobnosti.xlsx"))
demus_tab[is.na(demus_tab)] <- ""

@@

**DEMUS**: Osobnosti  
**MUSEION**: import_oo.csv

@@

modify_tab <- demus_tab %>% 
  filter(MTYPOSOSBY == "OO") %>% 
  mutate(MKODOS = str_trim(paste0(MPRIJM, " ", MJMENO))) %>% 
  mutate(MEMPTY = "") %>% 
  mutate('10osobaPohlavi' = "neznámé") %>% 
   # mutate('18subjektStatKod' = "CZ") %>% 
  mutate('42subjektSbirka' = sbirka) %>% 
  mutate('43subjektPodsbirka' = podsbirka)

@@

mus_tab <- modify_tab %>% 
  select('1typSubjektuKod' = MTYPOSOSBY,        # !! povinne !!
         '2subjektKod' = MKODOS,                # !! povinne !!
         '3subjektAlterKod' = MEMPTY, '4osobaJmenoPrvni'= MJMENO, 
         '5osobaJmenoDruhe' = MDRJMENO, 
         '6osobaPrijmeni' = MPRIJM,             # !! povinne !!
         '7osobaTitulPredJmenem' = MTITULPRED, '8osobaTitulZaJmenem' = MEMPTY, 
         '9osobaRodnePrijmeni' = MEMPTY, 
         '10osobaPohlavi' = '10osobaPohlavi',   # !! povinne !! "muž", "žena", "neznámé"
         '11osobaDatumNarozeni' = MEMPTY, '12osobaMistoNarozeni' = MistoNar_OS,
         '13okresNarozeniNazev' = MEMPTY, '14obecNarozeniNazev' = MEMPTY,
         '15statNarozeniKod' = MEMPTY, '16osobaDatumUmrti' = MEMPTY,
         '17osobaMistoUmrti' = MistoUmr_OS, '18subjektStatKod' = MEMPTY,
         '19kontaktEmail' = MEMPTY, '20kontaktMobil' = MEMPTY,
         '21kontaktMobil2' = MEMPTY, '22kontaktTelefon' = MEMPTY,
         '23kontaktInternet' = MEMPTY, '24kontaktInternetoveVolani' = MEMPTY,
         '25adresaText' = MEMPTY, '26kontaktniAdresaText' = MEMPTY,
         '27fyzickaOsobaRodneCislo' = MEMPTY, '28subjektPoznamka' = MEMPTY,
         '29AdresaTextoveOkres' = MEMPTY, '30AdresaTextoveObec' = MEMPTY,
         '31AdresaTextoveCastObce' = MEMPTY, '32AdresaTextoveMestskaCast' = MEMPTY,
         '33AdresaTextoveUlice' = MEMPTY, '34AdresaTextoveCisloOrientacni' = MEMPTY,
         '35AdresaTextoveCislo' = MEMPTY, '36AdresaTextovePSC' = MEMPTY,
         '37zamestnanecCislo' = MEMPTY, '38oddeleniKod' = MEMPTY,
         '39osobnostMedailon' = Medailon_OS, '40osobnostPseudonym' = MEMPTY,
         '41okruhSubjektuNazev' = MEMPTY,

@@

         '44osobaStudia' = MEMPTY,
         '45osobaSpolky' = MEMPTY, '46osobaOsobnost' = MEMPTY,
         '47subjektDatumOd' = DatNar_OS, '48subjektDatumDo' = DatUmr_OS,
         '49kontaktEmail2' = MEMPTY, 
         '50text1' = MEMPTY, '51text2' = MEMPTY, '52text3' = MEMPTY, 
         '53role1' = MEMPTY, '54role2' = MEMPTY, 
         '55role3' = MEMPTY, '56role4' = MEMPTY, '57$role5' = MEMPTY,
         rel_puvKOD = Jmeno_OS)

oper_oo <- mus_tab %>% 
  select(rel_puvKOD, '1typSubjektuKod', '2subjektKod', '4osobaJmenoPrvni', '6osobaPrijmeni')

# SAVE IMPORT FILE

save <- paste0(path_csv, spravce, "_import_oo.csv")

if(file.exists(save)){
  print("You've been here before!")
} else {
  write.table(mus_tab, file = save, 
            sep = ";", quote = T, row.names = F, 
            na = "", fileEncoding="cp1250")
  print("Written, baby!")
  }

@@

**DEMUS**: Osobnosti  
**MUSEION**: import_po.csv

@@

mus_tab <- modify_tab %>% 
  select(
    '1subjektKod' = '1subjektKod',          # !! povinne !!
    '2subjektAlterKod'= MEMPTY,
    '3pravnickaOsobaNazev' = Jmeno_OS,      # !! povinne !!
    '4pravnickaOsobaIC'= MEMPTY,
    '5pravnickaOsobaDIC' = MEMPTY, '6pravnickaOsobaZapsan'= MEMPTY,
    '7pravnickaOsobaFOP' = MEMPTY, '8subjektStatKod'= MEMPTY,
    '9kontaktEmail' = MEMPTY, '10kontaktMobil'= MEMPTY,
    '11kontaktMobil2' = MEMPTY, '12kontaktTelefon'= MEMPTY,
    '13kontaktInternet' = MEMPTY, '14kontaktInternetoveVolani'= MEMPTY,
    '15adresaText' = MEMPTY, '16kontaktniAdresaText'= MEMPTY,
    '17subjektPoznamka' = MEMPTY, '18AdresaTextoveOkres'= MEMPTY,
    '19AdresaTextoveObec' = MEMPTY, '20AdresaTextoveCastObce'= MEMPTY,
    '21AdresaTextoveMestskaCast' = MEMPTY, '22AdresaTextoveUlice'= MEMPTY,
    '23AdresaTextoveCisloOrientacni' = MEMPTY, '24AdresaTextoveCislo'= MEMPTY,
    '25AdresaTextovePSC' = MEMPTY,  '26subjektSbirka'= '26subjektSbirka',           
    '27subjektPodsbirka' = '27subjektPodsbirka', '28subjektDatumOd'= MEMPTY,
    '29subjektDatumDo' = MEMPTY, '30subjektMedailon'= Medailon_OS,
    '31okruhSubjektuNazev' = MEMPTY, '32kontaktEmail2'= MEMPTY,
    '33text1' = MEMPTY, '34text2'= MEMPTY,'35text3' = MEMPTY, 
    '36role1'= MEMPTY, '37role2' = MEMPTY, '38role3'= MEMPTY,
    '39role4' = MEMPTY, '40role5'= MEMPTY,
     rel_KODOS = Jmeno_OS)

oper_po <- modify_tab %>% 
  select(rel_puvKOD = Jmeno_OS, MTYPOSOSBY, '1subjektKod', nazev = Jmeno_OS)

# SAVE IMPORT FILE

save <- paste0(path_csv, spravce, "_import_po.csv")

if(file.exists(save)){
  print("You've been here before!")
} else {
  write.table(mus_tab, file = save, 
            sep = ";", quote = T, row.names = F, 
            na = "", fileEncoding="cp1250")
  print("Written, baby!")
  }

```
## AD + OO + PO (interni slovnik)

```{r JOIN AD+OO+PO IN ONE DICT}

ad <- oper_adresar %>% 
  mutate(typos = "AD",
         puvkod = rel_ZkrJm) %>% 
  rename(novykod = '2subjektKod',
         jmeno = '4osobaJmenoPrvni',
         prijm = '6osobaPrijmeni') %>% 
  select(typos, puvkod, novykod, jmeno, prijm)

oo <- oper_oo %>% 
  mutate(typos = "OO",
         puvkod = rel_puvKOD) %>% 
  rename(novykod = '2subjektKod',
         jmeno = '4osobaJmenoPrvni',
         prijm = '6osobaPrijmeni')%>% 
  select(typos, puvkod, novykod, jmeno, prijm)

po <- oper_po %>% 
  mutate(typos = "PO",
         puvkod = rel_puvKOD,
         prijm = "") %>% 
   rename(novykod = '1subjektKod',
         jmeno = nazev)%>% 
  select(typos, puvkod, novykod, jmeno, prijm)

interni_adresar <- bind_rows(ad, oo, po)

# SAVE FILE

save <- paste0(path_csv, "_", spravce, "_INTERNI_ADRESAR.csv")

if(file.exists(save)){
  print("You've been here before!")
} else {
  write.table(mus_tab, file = save, 
            sep = ";", quote = T, row.names = F, 
            na = "", fileEncoding="cp1250")
  print("Written, baby!")
  }

@@

**DEMUS**: Lokality  
**MUSEION**: import_lokalita.csv

@@

@@

# SAVE IMPORT FILE

save <- paste0(path_csv, spravce, "_import_lokalita.csv")

if(file.exists(save)){
  print("You've been here before!")
} else {
  write.table(mus_tab, file = save, 
            sep = ";", quote = T, row.names = F, 
            na = "", fileEncoding="cp1250")
  print("Written, baby!")
  }

@@

**DEMUS**: Materialy  
**MUSEION**: import_material.csv

@@

@@

# SAVE IMPORT FILE

save <- paste0(path_csv, spravce, "_import_material.csv")

if(file.exists(save)){
  print("You've been here before!")
} else {
  write.table(mus_tab, file = save, 
            sep = ";", quote = T, row.names = F, 
            na = "", fileEncoding="cp1250")
  print("Written, baby!")
  }

@@

**DEMUS**: Techniky  
**MUSEION**: import_technika.csv

@@

@@

# SAVE IMPORT FILE

save <- paste0(path_csv, spravce, "_import_technika.csv")

if(file.exists(save)){
  print("You've been here before!")
} else {
  write.table(mus_tab, file = save, 
            sep = ";", quote = T, row.names = F, 
            na = "", fileEncoding="cp1250")
  print("Written, baby!")
  }

@@

**DEMUS**: Nazvy 
**MUSEION**: import_oznaceni.csv

@@

@@

# SAVE IMPORT FILE

save <- paste0(path_csv, spravce, "_import_oznaceni.csv")

if(file.exists(save)){
  print("You've been here before!")
} else {
  write.table(mus_tab, file = save, 
            sep = ";", quote = T, row.names = F, 
            na = "", fileEncoding="cp1250")
  print("Written, baby!")
  }

@@

@@

**DEMUS**: Sbirky  
**MUSEION**: import_matpred.csv

@@

@@

# SAVE IMPORT FILE

save <- paste0(path_csv, spravce, "_import_matpred.csv")

if(file.exists(save)){
  print("You've been here before!")
} else {
  write.table(mus_tab, file = save, 
            sep = ";", quote = T, row.names = F, 
            na = "", fileEncoding="cp1250")
  print("Written, baby!")
  }

@@

**DEMUS**: Sbirky 
**MUSEION**: import_techpred.csv

@@

@@

# SAVE IMPORT FILE

save <- paste0(path_csv, spravce, "_import_techpred.csv")

if(file.exists(save)){
  print("You've been here before!")
} else {
  write.table(mus_tab, file = save, 
            sep = ";", quote = T, row.names = F, 
            na = "", fileEncoding="cp1250")
  print("Written, baby!")
  }

@@

tabulka s trojici ke konkretnimu predmetu
invc1 - 1. autor
invc1 - 2. datace
invc1 - 3. misto vzniku
invc1 - 4. autor 2
invc2 - 1. datace, atd

### kontrola rolí a lokalit

@@

```{r CHECK ROLES AND LOCS DICTIONARY}

@@

unique(oper_lokalita$'1lokalitaNazev')
unique(sbirky$MistoVz_S)

@@

**DEMUS**: Sbirky 
**MUSEION**: import_vznikPtu.csv

@@

```{r DERIVE VZNIKPTU FROM SBIRKY, warning = F, eval = F}

dopr_tab <- sbirky %>% 
  select(MINVC, Autor_S, Role_S, Datace_S, MistoVz_S) %>% 
  mutate(MEMPTY = "") %>% 
  mutate(MDATACE = Datace_S) %>%

  mutate(MDAT_Y = ifelse(str_detect(MDATACE, "_00_00"), MDATACE, "")) %>% 
  mutate(MDAT_Y = str_replace_all(MDAT_Y, "_00|-00", "")) %>%

  mutate(MDAT_YM = substring(ifelse(str_detect(MDATACE, "^([0-9]{4})[_]([0-9]{1})([1-9]{1})[_]00$"),
                                    MDATACE, ""), 1, 7)) %>% 
  mutate(MDAT_YM = format(anydate(MDAT_YM), "%m.%Y"))

@@

```{r CREATE CSV VZNIKPTU, eval = F}

@@

@@

# SAVE IMPORT FILE

save <- paste0(path_csv, spravce, "_import_vznikPtu.csv")

if(file.exists(save)){
  print("You've been here before!")
} else {
  write.table(mus_tab, file = save, 
            sep = ";", quote = T, row.names = F, 
            na = "", fileEncoding="cp1250")
  print("Written, baby!")
  }

@@

**DEMUS**: Sbirky 
**MUSEION**: import_obp.csv

@@

    '115rokPrirust' = MEMPTY,'116mnozstviSlovy' = MEMPTY,
    '117pocetCasti' = MEMPTY,'118popisCasti' = MEMPTY)

@@

# SAVE IMPORT FILE

save <- paste0(path_csv, spravce, "_import_obp.csv")

if(file.exists(save)){
  print("You've been here before!")
} else {
  write.table(mus_tab, file = save, 
            sep = ";", quote = T, row.names = F, 
            na = "", fileEncoding="cp1250")
  print("Written, baby!")
}

@@

# SAVE IMPORT FILE

save <- paste0(path_csv, spravce, "_import_obp_CVICNE.csv")

if(file.exists(save)){
  print("You've been here before!")
} else {
  write.table(mus_tab, file = save, 
            sep = ";", quote = T, row.names = F, 
            na = "", fileEncoding="cp1250")
  print("Written, baby!")
  }
```

@@

**DEMUS**: Sbirky 
**MUSEION**: import_par.csv

@@

write.table(mus_tab, paste0(path_csv, project, "_import_par.csv"), 
            sep = ";", quote = T, row.names = F, 
            na = "", fileEncoding="cp1250")
```

@@

**DEMUS**: Sbirky 
**MUSEION**: import_vum.csv

@@

write.table(mus_tab, paste0(path_csv, project, "_import_vum.csv"), 
            sep = ";", quote = T, row.names = F, 
            na = "", fileEncoding="cp1250")

@@

**DEMUS**: Sbirky 
**MUSEION**: import_fot.csv

@@

write.table(mus_tab, paste0(path_csv, project, "_import_fot.csv"), 
            sep = ";", quote = T, row.names = F, 
            na = "", fileEncoding="cp1250")

@@

**DEMUS**: Sbirky 
**MUSEION**: import_bio.csv

@@

write.table(mus_tab, paste0(path_csv, project, "_import_bio.csv"), 
            sep = ";", quote = T, row.names = F, 
            na = "", fileEncoding="cp1250")

@@

**DEMUS**: Sbirky 
**MUSEION**: import_br.csv

@@

    '39nominaceRok' = MEMPTY, '40nominaceKategorie' = MEMPTY,
    '41oceneniRok' = MEMPTY, '42oceneniKategorie' = MEMPTY,
    '43oceneniMisto' = MEMPTY, '44oceneniTyp' = MEMPTY,
    '45variantaCCLicenceOznaceni' = MEMPTY, '46seznamKontextovychDokumen' = MEMPTY) 
# %>% 
#   mutate_all( ~ str_replace_all(., pattern = ";", replacement = " ")) %>%  # removes semicolons
#   mutate_all( ~ str_replace_all(., pattern = "[\r\n]", replacement = " ")) #removes paragraphs

@@

write.table(mus_tab, paste0(path_csv, project, "_import_br.csv"), 
            sep = ";", quote = T, row.names = F, 
            na = "", fileEncoding="cp1250")
```

@@

# p i s k o v i s t e

```{r CHECK LOCS DICTIONARY}

unique(oper_lokalita$'1lokalitaNazev')
unique(sbirky$MistoVz_S)

# SAVE IMPORT FILE

save <- paste0(path_csv, spravce, "_import_lokalita_mistvzn.csv")

if(file.exists(save)){
  print("You've been here before!")
} else {
  write.table(mvzn, file = save, 
            sep = ";", quote = T, row.names = F, 
            na = "", fileEncoding="cp1250")
  print("Written, baby!")
  }
